---
title: "Write-up"
author: "samuel mao"
date: "July 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(shiny)
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(markdown)
library(leaflet)
library(shinydashboard)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(wesanderson)
library(ggthemes)
library(gridExtra)
#setwd("C:/Users/samuelmao/Desktop/DataScience/Project1/Project1")
#read data into global.R
ks18<-fread(file = "./ks18.csv",sep = ',',fill=TRUE)
bycountry<-fread(file="./bycountry.csv")
withoutlive<-ks18%>%filter(state!="live",region=="United States")%>%group_by(main_category)%>%summarize(rate=sum(state=="successful")/n())
successful_scatter<-ks18%>%filter(state!="live",region=="United States")%>%group_by(main_category)%>%summarize(projects=n(),successful_projects=sum(state=="successful"))

piedata<-ks18%>%summarise(US_Observation=sum(region=="United States"), Rest_Observation=sum(region!="United States"))
piedata2<-gather(piedata,key=region,value=observation, US_Observation,Rest_Observation)


```

## Kickstarter project overview

Kickstarter is essentially an online market that has both creator and supporter. For an online market to grow, one of the most important feature that cannot be ignored is the "Network effect". This means that Kickstarter needs to grow both its number of creators and number of supportors. A creator is someone or some company that has an idea that needs funding to let it come to fruition. A supporter is an online user on the Kickstarter who decides to contribute his or her money for the project created by the creator. Because Kickstarter makes money when a project is successfully funded (5% of the money funded goes to the platform according to Investopedia), it is very important for Kickstarter to make sure a creator's project meets the funding goal. Therefore, the aim of this project is to help both creator and the platform to increase success rate and therefore revenue by answering questions such as:

* Which category has the highest success rato by date?
* Which category has the most project listed?
* What are the common themes in project names for each category?
* How much does a project ask for, and whether if the amount asked would influence the outcome
* How many projects are listed from outside of United States, and what are those projects like?

Once these fundamental questions can be answered, further machine learning techinique could help unearth information such as:

* What are the similarities between successful project and unsuccessful project?
* What are the similiarities of projects within a cateogry and across category?
* What are the main factors that influence a project outcome?

There are some key information for each project that are not recorded by the dataset, such as the project information provided by the creator under their project page. The design of each project page could usually influence a supporter's decision. However, the current dataset contains 16 columns and more than 300,000 records by date, and thus the dataset is rich enough to dig up some key insights.

More information about Kickstart is here:<http://rmarkdown.rstudio.com> .
The data for this project is from Kaggle collected by Mickaël Mouillé from mid 2011 to early 2018: <https://www.kaggle.com/kemical/kickstarter-projects>

#Users on Kickstart
There are almost 300,000 projects listed in the United States, comparing to a total number of 378,611 records in our collected databse. It represents a significant portion on the Kickstarter. The contries that follow behind are UK and Canada, both English speaking countries. In




#United States, Fund amount:


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
